Slightly Positive Correlation Between Racialization, Gendering and Police Strip Searches in the Toronto Municipal, 2020-2021

### 2024-01-26 outputs/paper/paper.qmd
final polish of appendix and paper

```{r fig.height=7, fig.width=9, fig.pos='H'}
#| echo: false
#| message: false
#| label: fig-race-gender-search
#| fig-cap: Racial Identities and Police Strip Search Per Arrest in Toronto, 2020-2021

  ggplot(mapping = aes(x = race, fill = strip_search), data=cleaned_race_gender_data) +
  geom_bar() + 
  labs(y = "Count", x = "Race", fill = "Strip Search") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  facet_wrap(~gender) + scale_fill_viridis_d(option="cividis")

@@

>>>>

```{r fig.height=7, fig.width=9, fig.pos='H'}
#| echo: false
#| message: false
#| label: fig-race-gender-search
#| fig-cap: Racial Identities and Police Strip Search Per Arrest in Toronto, 2020-2021
cleaned_male_female_data <-
  cleaned_race_gender_data |>
  filter(gender != "U")

  ggplot(mapping = aes(x = race, fill = strip_search), data=cleaned_male_female_data) +
  geom_bar() + 
  labs(y = "Count", x = "Race", fill = "Strip Search") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  facet_wrap(~gender) + scale_fill_viridis_d(option="cividis")

@@

@tbl-items-strip-search conveys the total number of strip searches happening in Toronto from 2020 to 2021, and whether or not items were found during each search.
